{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-11 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@

                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 

@@

                    + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 

@@

            \item $\sigma^{(k)}$ be another list of i.i.d random variable. 
            \item $\tilde \mu \ge 0$ be a constant that is fixed.

@@

        Then for all $\bar x \in \RR^m, k \ge 1$, the iterates satisfies the inequality: 

@@

                + \frac{L_k\alpha_k^2}{2} \left\Vert \left(I - \Pi^{(i)}\right)(\bar x - v_k)\right\Vert^2

@@

                    \left\Vert \left(I - \Pi^{(i)}\right)(v_{k - 1} - \bar x)\right\Vert^2

@@

@@

        Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
        Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
        The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next. 

@@

            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{i} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}. 

@@

@@

                0 &\le F_i(z_k) - F_i(x_k) - 

@@

                + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert (I - \Pi^{(i)}) (z_k - y_k)\right\Vert^2

@@

                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert (I - \Pi^{(i)})(\bar x - x_{k - 1})\Vert^2
                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert (I - \Pi^{(i)})(z_k - y_k)\Vert^2

@@

        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_{\bullet} = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_\bullet := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well. 

@@

            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\bullet

@@

            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

                \right\Vert^2_\bullet
            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 
                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet

@@

            \right)\Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

                \right) \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet

@@

            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_\bullet

@@

                \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet

@@

                \Vert \bar x - x_{k - 1}\Vert^2_\bullet 
                + \Vert \bar x - v_{k - 1}\Vert^2_\bullet 
                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet

@@

                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet.

@@

        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-s1-chain1} it gives: 

@@

                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet

@@

                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet
                \\ & \quad

@@

                    F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \right) + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2

@@

        Re-arranging, with some linear algebra:  we get out first result: 
            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_\bullet 
            F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet
        For the first inequality, recall that $\Vert \cdot\Vert_\bullet = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$. 

@@

@@

            \item If, each $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, then for all $\bar x \in \RR^m$, $k \ge 1$ it satisfies the inequality: 

@@

                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.

@@

            \item If we choose $\bar x \in \Pi_{\ker A^{(i)}}(y_k)$, then for all $k \ge 1$ it has

@@

>>>>

    When two expressions are connected via non-trivial results, it's expressed with $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ where $(\cdot)$ is a label of some intermediate results immediately before it, or explained right after a chain of expressions. 

@@

                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert z - x\Vert^2
                    + \frac{\mu\sigma_{\min}(A)^2}{2}\Vert \Pi(z - x)\Vert^2. 

@@

                        + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert \Pi(z - x)\Vert^2
                        + \frac{\sigma_{\min}(A)^2}{2}\Vert \Pi(z - x)\Vert^2
                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert z - x\Vert^2
                    + \frac{\mu\sigma_{\min}(A)^2}{2}\Vert \Pi(z - x)\Vert^2.

@@

            \item $\sigma^{(I_k)}$ be another list of i.i.d random variable, 
            \item $\tilde \mu \ge 0$ be a constant that is fixed, 

@@

        For all $\bar x \in \RR^m, k \ge 1$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
        Then, the iterates satisfy: 

@@

                & F_i(x_k) - F_i(\bar x)
                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
                \\&\le 

@@

                    F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
                \right) + \mathcal R_k^{(i)}. 

@@

        Where: 
            & \mathcal R_k^{(i)} = (1 - \alpha_k)\left(
                \frac{\sigma^{(i)}\alpha_k}{2}\left\Vert \Pi^{(i)} (\bar x - x_{k - 1})\right\Vert^2
                - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                + \frac{\sigma^{(i)}}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2. 

@@

@@

            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{(i)} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}. 

@@

        \textbf{For simpler notations}
        \begin{itemize}[nosep]
            \item We use $\langle \cdot,\cdot\rangle_\sharp := \langle H(\cdot), H(\cdot)\rangle$ for any linear mapping $H$, and denote $\Vert x\Vert_{\sharp} = \sqrt{\langle x, x\rangle_\sharp}$. 
            \item We denote specifically $\Vert \cdot\Vert_\bullet$ for the semi norm $\Vert (I - \Pi^{(i)})(\cdot)\Vert$, and $\Vert \cdot\Vert_{\circ}$ for the semi norm $\left\Vert \Pi^{(i)} x\right\Vert$. So it has $\Vert x\Vert^2_\circ + \Vert x\Vert^2_\bullet = \Vert x\Vert^2$. 

@@

                0 &\underset{\text{(a)}}{\le} F_i(z_k) - F_i(x_k) - 

@@

                + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2
                    + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2_\circ

@@

                + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert z_k - y_k\Vert^2
                & = 
                + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                    + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert z_k - y_k\Vert^2
                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2

@@

@@

            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp
            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\sharp

@@

            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp

@@

                \right\Vert^2_\sharp
            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp 
                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_\sharp 
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp

@@

            \right)\Vert \bar x - x_{k - 1}\Vert^2_\sharp

@@

                \right) \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp

@@

            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_\sharp

@@

            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_\sharp

@@

                \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp

@@

                \Vert \bar x - x_{k - 1}\Vert^2_\sharp 
                + \Vert \bar x - v_{k - 1}\Vert^2_\sharp 
                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp

@@

                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\sharp
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp.

@@

        So, this is our results: 
        \begin{align}\begin{split}\label{eqn:snapg2-one-spte-s1-chain2}
            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp
            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\sharp
                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\sharp
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp.
        Substituting the above back to the tail of \eqref{ineq:snapg2-one-step-s1-chain1} for $\Vert \cdot\Vert_\sharp = \Vert \cdot\Vert$ it has: 

@@

                + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                    + \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
                    + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
                    \Vert x_{k - 1} - v_{k - 1} \Vert^2
                    + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

            + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                + \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                F_i(x_k) - F_i(\bar x)
                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
                + (1 - \alpha_k)\left(
                    \frac{\sigma^{(i)}\alpha_k}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
                    - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

        Define
            & \mathcal R_k^{(i)} := (1 - \alpha_k)\left(
                \frac{\sigma^{(i)}\alpha_k}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
                - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2. 
        Then the result can be written as: 
            & F_i(x_k) - F_i(\bar x)
                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
            \\&\le 

@@

                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
            \right) + \mathcal R_k^{(i)}. 

@@

        If at least one of the followings is true: 

@@

            \item For all $i = 1, \ldots, n$ it has $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, Let $\bar x \in \RR^m$ be arbitrary;
            \item Assume $x_{k - 1}, v_{k - 1}$ are in $\left(\ker A^{(i)}\right)^\perp$, let $\bar x \in \left(\ker A^{(i)}\right)^{\perp}$ be arbitrary. 
        Then for all $k \ge 1$ it has: 

@@

                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2

@@

        And when $k = 0$, we have \eqref{ineq:snagp2-one-step-s1-rslt2} as well. 

@@

        Firstly take note that from Lemma \ref{lemma:snagp2-one-step-s1} using the fact that $\Pi^{(i)}$ is a projection matrix it has directly: 
            & F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert (I - \Pi^{(i)})( v_{k - 1} - \bar x)\right\Vert^2
                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert v_{k - 1} - \bar x\right\Vert^2
                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
        Next, we will show that $\Pi^{(i)}(z_k - y_k)$ is zero under item (i), (ii). 
        Let's prove (i) first. 
        Since $A^{(i)} = I$, its kernel is zero hence the $\Pi^{(i)}$ in Lemma \ref{lemma:snagp2-one-step-s1} projects to $\{0\}$ and the term $\Pi^{(i)}(z_k - y_k) = \mathbf 0$ in \eqref{ineq:snagp2-one-step-s1-rslt1}. It's done. 
        To see (ii), recall that $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$ from Lemma \ref{lemma:snagp2-one-step-s1}, obviously $z_k \perp \ker A^{(i)}$ as well. 
        Recall that $y_k$ as defined in Definition \ref{def:snapg-v2-proto} has
            y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}.
        So $y_k \perp \ker A^{(i)}$ because it's the linear combinations of $v_{k - 1}, x_{k - 1}$. 
        Hence, the projection of $y_k, z_k$ onto $\ker A^{(i)}$ by $\Pi^{(i)}$ is zero, hence the results from Lemma \ref{lemma:snagp2-one-step-s1} simplifies as well. 
